Recurrent Neural Networks for object detection

### 2019-07-16 Paper/Paper_First_Draft.tex
Reworked in Section 3-c

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks}
In [4] Tripathi, Lipton, Belongie, Nguyen come up with a neural network architecture for video-based object detection. Their architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset. \newline

The final architecture can be found in \textbf{Fig 2}. Tripathi, Lipton and Belongie first train the pseudo-labeler, which is an YOLO object detection network originally trained for 20-class PASCAL VOC on the YouTube-Video Dataset. As specified in YOLO [] they minimize the weighted squared detection loss and optimize classification and localization error simultaneously.

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks}
\end{figure}

After training the pseudo-labeler they train the Recurrent Neural Network, which takes as an input the pseudo-labels and outputs improved prediction. The RNN consists of two GRU layers. \newline

For training the whole network they use the following loss function to take both accuracy at the target frame and consistency of predictions across adjacent time steps into consideration: \newline

@@

For the final output Tripathi, Lipton, Belongie and Nguygen use the object detection loss as described in YOLO []:

@@

The similarity loss considers the dissimilarity between the pseudo-labels and prediction at each frame t:

The category loss takes wrong class probabilities into consideration:

@@

And the prediction-consistency loss regularizes the model by encouraging smoothness predictions across the time-steps:

@@

During the evaluation they find two possible areas of improvement for their approach. On the one hand the RNN is not able to recover from wrong predictions made by the pseudo-labeler after they have been fed into the RNN.  On the other hand, they observe that their network is not robust to motion.

@@

\begin{thebibliography}{00}
\bibitem{b1} Alexander Broad, Michael Jones, Teng-Yok Lee. Recurrent Multi-frame Single Shot Detector for Video Object Detection. 2018.
\bibitem{b2} Mason Liu, Menglong Zhu. Mobile Video Object Detection with Temporally-Aware Feature Maps. 2018.
\bibitem{b3} Xizhou Zhu, Yuwen Xiong, Jifeng Dai, Lu Yuan, Yichen Wei. Deep Feature Flow for Video Recognition. 2017.
\bibitem{b4} Subarna Tripathi, Zachary C. Lipton, Serge Belongie, Truong Nguyen. Context Matters: Refining Object Detection in Video with Recurrent Neural Networks.
\bibitem{b5} Guanghan Ning, Zhi Zhang, Chen Huang, Zhihai He, Xiaobo Ren, Haohong Wang. Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking. 2016.
\bibitem{b6} Kai Yi, Zhiqiang Jian, Shitao Chen, Nanning Zheng. Feature Selective Small Object Detection via Knowledge-based Recurrent Attentive Neural Network. 2019.
\bibitem{b7} Mason Liu, Menglong Zhu, Marie White, Yinxiao Li, Dmitry Kalenichenko. Looking Fast and Slow: Memory-Guided Mobile Video Object Detection. 2019.
\bibitem{b8} Christoph Feichtenhofer, Axel Pinz, Andrew Zisserman. Detect to Track and Track to Detect. 2017.
\bibitem{b9} Kai Kang, Wanli Ouyang, Hongsheng Li, Xiaogang Wang. Object Detection from Video Tubelets with Convolutional Neural Networks. 2016.
\bibitem{b10} Kai Chen, Jiaqi Wang, Shuo Yang, Xingcheng Zhang, Yuanjun Xiong, Chen Change Loy, Dahua Lin. Optimizing Video Object Detection via a Scale-Time Lattice. 2018.
\bibitem{b11} Ian Goodfellow, Yoshua Bengio, Aaron Courville. Deep Learning (Adaptive Computation and Machine Learning). 2017.
\bibitem{b12} Alexander Broad, Michael Jones, Teng-Yok Lee. Supplementary Material for Recurrent Multi-frame Single Shot Detector for Video Object Detection. 2018.
\bibitem{b13} Jia Deng, Wei Dong, Richard Socher, Li-Jia Li, Kai Li and Li Fei-Fei. ImageNet: A Large-Scale Hierarchical Image Database. 
\bibitem{b14} Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton. ImageNet Classification with Deep Convolutional Neural Networks. 2012.
\bibitem{b15} Shaoqing Ren, Kaiming He, Ross Girshick, Jian Sun. Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks. 2016. 
\bibitem{b16} Joseph Redmon, Ali Farhadi. YOLOv3: An Incremental Improvement.
\bibitem{b17} Wei Liu, Dragomir Anguelov, Dumitru Erhan, Christian Szegedy, Scott Reed, Cheng-Yang Fu, Alexander C. Berg. SSD: Single Shot MultiBox Detector. 2016.
\bibitem{b18} Sepp Hochreiter, Jürgen Schmidhuber. Long short-term memory In: Neural Computation (journal), vol. 9, issue 8, p. 1735-1780. 1997.
\bibitem{b19} J. Dai, Y. Li, K. He, and J. Sun. R-FCN: Object detection via
region-based fully convolutional networks. In NIPS, 2016.
\bibitem{b20} Jonathan Huang, Vivek Rathod, Chen Sun, Menglong Zhu, Anoop Korattikara, Alireza Fathi, Ian Fischer, Zbigniew Wojna, Yang Song, Sergio Guadarrama, et al.. Speed/accuracy trade-offs for modern convolutional object detectors . In \textit{Proceedings of the Conference on Computer Vision and Pattern Recognition (CVPR}, 2017.
\bibitem{b21} Andreas Geiger, Philip Lenz and Raquel Urtasun. Are we ready for autonomous driving? The kitti vision benchmark suite. In \textit{Conference on Computer Vision and Patern Recognition (CVPR)}, 2012.
\bibitem{b22} P. Dollár, C. Wojek, B. Schiele and P. Perona. Pedestrian detection: A benchmark. In \textit{Proceedings of the Conference on Computer Vision and Pattern Recognition (CVPR)}, June 2009.
\bibitem{b23} Bichen Wu, Forrest Iandola, Peter H. Jin, Kurt Keutzer. SequeezeDet: Unified, Small, Low Power Fully Convolutional Neural Networks for Real-Time Object Detection for Autonomous Driving. In CVPR \textit{Workshops}, 2017.
\bibitem{b24} A. Howard, M. Zhu, B. Chen, D. Kalenichenko, W. Wang, T. Weyand, M. Andreetto, H. Adam. Mobilenets: Efficient convolutional neural networks for mobile vision applications. \textit{arXiv preprint arXiv:1704.04861}, 2017.
\end{thebibliography}
\vspace{12pt}

>>>>

\subsection{Context Matters: Refining Object Detection in Video with Recurrent Neural Networks [3]}
In [4] Tripathi, Lipton, Belongie, Nguyen come up with a neural network architecture for video-based object detection. Their architecture consists two parts: A pseudo-labeler, which assigns labels to all video frames and a recurrent unit which refines those pseudo-labels by using the contextual information. Moreover, they describe a training strategy for their architecture and compare their approach to other models on the YouTube-Objects dataset (v2.0), which consists of the ten categories airplane, bird, boat, car, cow, dog, horse, mbike, train. Their model reaches an mAP of 68.73 percent which improves the strongest image-based baseline for Youtube-Video Objects dataset of 7.1\% [4-Abstract; 25]. \newline

The final architecture can be found in \textbf{Fig 2}. Tripathi, Lipton and Belongie first train the pseudo-labeler, which is an YOLO object detection network [26] originally trained for 20-class PASCAL VOC [27] on the YouTube-Video Dataset. As specified in YOLO  they minimize the weighted squared detection loss and optimize classification and localization error simultaneously [4-3].

\begin{figure} [h]
\includegraphics[width=\columnwidth]{ContextMatters}
\caption{Architecture Context Matters: Refining Object Detection in Video with Recurrent Neural Networks [4]. First the "Pseudolabler" creates bounding boxes and class probabilities for every input frame. Afterwards the GRU fuses the output of the current and some past frames and refines the bounding boxes and class probabilities.}
\end{figure}

After training the pseudo-labeler they train the Recurrent Neural Network, which takes as an input the pseudo-labels and outputs improved prediction. The RNN consists of two GRU layers [4-2]. \newline

For training the whole network they use the following loss function to take both accuracy at the target frame and consistency of predictions across adjacent time steps into consideration. They choose the values of $\alpha = 0.2$, $\beta = 0.2$ and $\gamma = 0.1$ based on the detection performance on the validation set [4-2.1]: \newline

@@

For the final output Tripathi, Lipton, Belongie and Nguygen use the object detection loss as described in YOLO [26, 4-2.1.1]: \newline

$ detection_{loss} = \lambda_{corr} $ \textit{todo}

The similarity loss considers the dissimilarity between the pseudo-labels and prediction at each frame t [4-2.1.2]: \newline

@@

The category loss takes wrong class probabilities into consideration [4-2.1.3]:

@@

And the prediction-consistency loss regularizes the model by encouraging smoothness predictions across the time-steps [4-2.1.4]:

@@

During the evaluation they find two possible areas of improvement for their approach. On the one hand the RNN is not able to recover from wrong predictions made by the pseudo-labeler after they have been fed into the RNN.  On the other hand, they observe that their network is not robust to motion [4-3.4].

Tripathi, Lipton, Belongie and Nguyen test their model on the Youtube-Objects dataset. Overall they outperform the best no-recurrent architecture (DA Yolo) in their comparison by 7\% mAP. It's notable that DA YOLO reaches gut results in detection of airplanes and birds but comparatively bad result in detection of cats, cows, dogs, horses and mbike. In those categories the recurrent networks in the comparison outperform the non-recurrent ones [4-3.1]. \newline

The architecture mentioned in "Context Matters: Refining Object Detection in Video with Recurrent Neural Networks" is pretty similar to the one used in [4]. Both are using the YOLO network architecture as a baseline and feed its output into an Recurrent Unit. Main Differences is that [4] feeds the bounding boxes and in addition some visual features into the recurrent unit.

@@

\begin{thebibliography}{00}
\bibitem{b1} Alexander Broad, Michael Jones, Teng-Yok Lee. Recurrent Multi-frame Single Shot Detector for Video Object Detection. 2018.
\bibitem{b2} Mason Liu, Menglong Zhu. Mobile Video Object Detection with Temporally-Aware Feature Maps. 2018.
\bibitem{b3} Xizhou Zhu, Yuwen Xiong, Jifeng Dai, Lu Yuan, Yichen Wei. Deep Feature Flow for Video Recognition. 2017.
\bibitem{b4} Subarna Tripathi, Zachary C. Lipton, Serge Belongie, Truong Nguyen. Context Matters: Refining Object Detection in Video with Recurrent Neural Networks.
\bibitem{b5} Guanghan Ning, Zhi Zhang, Chen Huang, Zhihai He, Xiaobo Ren, Haohong Wang. Spatially Supervised Recurrent Convolutional Neural Networks for Visual Object Tracking. 2016.
\bibitem{b6} Kai Yi, Zhiqiang Jian, Shitao Chen, Nanning Zheng. Feature Selective Small Object Detection via Knowledge-based Recurrent Attentive Neural Network. 2019.
\bibitem{b7} Mason Liu, Menglong Zhu, Marie White, Yinxiao Li, Dmitry Kalenichenko. Looking Fast and Slow: Memory-Guided Mobile Video Object Detection. 2019.
\bibitem{b8} Christoph Feichtenhofer, Axel Pinz, Andrew Zisserman. Detect to Track and Track to Detect. 2017.
\bibitem{b9} Kai Kang, Wanli Ouyang, Hongsheng Li, Xiaogang Wang. Object Detection from Video Tubelets with Convolutional Neural Networks. 2016.
\bibitem{b10} Kai Chen, Jiaqi Wang, Shuo Yang, Xingcheng Zhang, Yuanjun Xiong, Chen Change Loy, Dahua Lin. Optimizing Video Object Detection via a Scale-Time Lattice. 2018.
\bibitem{b11} Ian Goodfellow, Yoshua Bengio, Aaron Courville. Deep Learning (Adaptive Computation and Machine Learning). 2017.
\bibitem{b12} Alexander Broad, Michael Jones, Teng-Yok Lee. Supplementary Material for Recurrent Multi-frame Single Shot Detector for Video Object Detection. 2018.
\bibitem{b13} Jia Deng, Wei Dong, Richard Socher, Li-Jia Li, Kai Li and Li Fei-Fei. ImageNet: A Large-Scale Hierarchical Image Database. 
\bibitem{b14} Alex Krizhevsky, Ilya Sutskever, Geoffrey E. Hinton. ImageNet Classification with Deep Convolutional Neural Networks. 2012.
\bibitem{b15} Shaoqing Ren, Kaiming He, Ross Girshick, Jian Sun. Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks. 2016. 
\bibitem{b16} Joseph Redmon, Ali Farhadi. YOLOv3: An Incremental Improvement.
\bibitem{b17} Wei Liu, Dragomir Anguelov, Dumitru Erhan, Christian Szegedy, Scott Reed, Cheng-Yang Fu, Alexander C. Berg. SSD: Single Shot MultiBox Detector. 2016.
\bibitem{b18} Sepp Hochreiter, Jürgen Schmidhuber. Long short-term memory In: Neural Computation (journal), vol. 9, issue 8, p. 1735-1780. 1997.
\bibitem{b19} J. Dai, Y. Li, K. He, and J. Sun. R-FCN: Object detection via
region-based fully convolutional networks. In NIPS, 2016.
\bibitem{b20} Jonathan Huang, Vivek Rathod, Chen Sun, Menglong Zhu, Anoop Korattikara, Alireza Fathi, Ian Fischer, Zbigniew Wojna, Yang Song, Sergio Guadarrama, et al.. Speed/accuracy trade-offs for modern convolutional object detectors . In \textit{Proceedings of the Conference on Computer Vision and Pattern Recognition (CVPR}, 2017.
\bibitem{b21} Andreas Geiger, Philip Lenz and Raquel Urtasun. Are we ready for autonomous driving? The kitti vision benchmark suite. In \textit{Conference on Computer Vision and Patern Recognition (CVPR)}, 2012.
\bibitem{b22} P. Dollár, C. Wojek, B. Schiele and P. Perona. Pedestrian detection: A benchmark. In \textit{Proceedings of the Conference on Computer Vision and Pattern Recognition (CVPR)}, June 2009.
\bibitem{b23} Bichen Wu, Forrest Iandola, Peter H. Jin, Kurt Keutzer. SequeezeDet: Unified, Small, Low Power Fully Convolutional Neural Networks for Real-Time Object Detection for Autonomous Driving. In CVPR \textit{Workshops}, 2017.
\bibitem{b24} A. Howard, M. Zhu, B. Chen, D. Kalenichenko, W. Wang, T. Weyand, M. Andreetto, H. Adam. Mobilenets: Efficient convolutional neural networks for mobile vision applications. \textit{arXiv preprint arXiv:1704.04861}, 2017.
\bibitem{b25} Alexander Prest, Vicky Kalogeiton, Christian Leistner, Javier Civera, Cordelia Schmid, Vittorio Ferrari. Youtube-objects dataset v2.0, 2014. URL calvin.inf.ed.ac.uk/datasets/youtube-objects-datasets. University of Edinbough (CALVIN), INRIA Grenoble (LEAR), ETH Zurich (CALVIN). 
\bibitem{b26} Joseph Redmon, Santosh Kumar Divvala, Ross B. Girshink, Ali Farhadi. You only look once: Unified, real-time object detection, \textit{in CVPR 2016}.
\bibitem{b27} Mark Everingham, Luc Gool, Christopher K. Williams, John Winn and Andrew Zisserman. The pascal visual object classes (voc) challenge. \textit{Int. J. Comput. Vision}, 88(2):303-338, June 2010, ISSN 0920-5691
\end{thebibliography}
\vspace{12pt}
